\documentclass[a4paper]{article}

\usepackage{geometry}
\geometry{a4paper,left=25mm,right=25mm, top=0.5cm, bottom=0.8cm} 
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{lastpage}

%opening
\title{Orange Management}
\author{Confidentiality Agreement regarding the project "Orange Management" \\ and it's management}
\date{}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

\begin{document}

\maketitle

\section{Definition}
As used herein, "Confidential Information" refers to any information which has commercial value and is either

\begin{itemize}
\item technical information, including patent, copyright, trade secret, and other proprietary information, techniques, sketches, drawings, models, inventions, know-how, processes, apparatus, equipment, algorithms, software programs, software source documents, and formulae related to the current, future and proposed products and services regarding "Orange Management", or 
\item non-technical information relating to "Orange Management" products, including without limitation pricing, margins, merchandising plans and strategies, finances, financial and accounting data and information, suppliers, customers, customer lists, purchasing data, sales and marketing plans, future business plans and any other information which is proprietary and confidential to this project.
\end{itemize}

\section{Non-disclosure and Non-use Obligations}
Recipient will maintain in strict confidence and will not disclose, disseminate or use any Confidential Information belonging to "Orange Management", whether or not in written form. If Recipient is not an individual, Recipient agrees that Recipient shall disclose Confidential Information only to those who need to know such information, and certifies that such are bound by a confidentiality agreement.

\section{Survival}
This Agreement shall govern all communications between the parties. Recipient understands that its obligations under section 2 shall survive the termination of any other relationship between the parties. Upon termination of any relationship, Recipient will promptly deliver to "Orange Management" (without retaining any copies) all documents and other materials furnished to Recipient by "Orange Management".

\section{Governing Law and Jurisdiction}
This Agreement shall be governed exclusively by German law. The courts of Hessen, Germany shall have exclusive jurisdiction.

\section{Injunctive Relief}
A breach of any of the promises or agreements contained herein will result in irreparable and continuing damage to "Orange Management" for which there will be no adequate remedy at law. The management of "Orange Management" shall be entitled to injunctive relief and / or a decree of specific performance, and such other relief as may be proper (including monetary damages if appropriate).

\section{Entire Agreement}
This Agreement constitutes the entire agreement with respect to the Confidential Information disclosed herein and supersedes all prior or contemporaneous oral or written agreements concerning such Confidential Information. This Agreement may only be changed by mutual agreement of authorized representatives of the parties in writing. \newline

I HAVE READ THE TERMS OF THIS AGREEMENT AND AGREE FULLY WITH THE SAME.\newline

\begin{tabular}{ l l l r }
Date: & \hspace{0.7cm} \makebox[1.5in]{\hrulefill} & Name: & \hspace{1.0cm} \makebox[2.0in]{\hrulefill} \\
& & & \\
& & Signature: & \hspace{0.4cm} \makebox[2.0in]{\hrulefill}
\end{tabular}

\vfill
\begin{center}
Page \thepage\ of \pageref{LastPage}
\end{center}
\end{document}